% resume.tex
%
% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003-2007 David J. Grant <davidgrant-at-gmail.com> http://www.davidgrant.ca
%
% This work is licensed under the Creative Commons Attribution-ShareAlike 3.0 Unported License. To view a copy of this license, visit http://creativecommons.org/licenses/by-sa/3.0/ or send a letter to Creative Commons, 171 Second Street, Suite 300, San Francisco, California, 94105, USA.

\documentclass[letterpaper,11pt]{article}

%-----------------------------------------------------------
%Margin setup

\setlength{\voffset}{0.1in}
\setlength{\paperwidth}{8.5in}
\setlength{\paperheight}{11in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
\setlength{\textheight}{11in}
\setlength{\textheight}{9.5in}
\setlength{\topmargin}{-0.25in}
\setlength{\textwidth}{7in}
\setlength{\topskip}{0in}
\setlength{\oddsidemargin}{-0.25in}
\setlength{\evensidemargin}{-0.25in}
%-----------------------------------------------------------
%\usepackage{fullpage}
\usepackage{shading}
%\textheight=9.0in
\pagestyle{empty}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\large \parashade[.9]{sharpcorners}{\textbf{#1 \vphantom{p\^{E}}}}}}
\newcommand{\ressubheading}[4]{
    \begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}
%-----------------------------------------------------------


\begin{document}

\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
\textbf{\huge Alex Burkey}  & 703-342-9945\\
 &  alex.w.burkey@gmail.com \\
 & alexburkey.com\\
\end{tabular*}

\resheading{Work Experience}
\vspace{-0.2in}
\begin{itemize}
\item[]
	\ressubheading{Stripe}{Denver, CO}{Infrastructure Engineer}{Nov 2021 -- June 2023}
	\begin{itemize}
        \resitem{Removed +10 million DB calls per day, reduced Airflow incidents and reduced Airflow task startup time by refactoring dependency graph compilation.}
	    
        \resitem{Prevented RDS instance from running out of client connections as Airflow worker cluster scaled by creating a containerized connection pooling service}
	    
	    \resitem{Saved 10\% on EC2 costs by migrating multiple Airflow Worker clusters to use EBS instead of on-instance storage.}
	    
	\end{itemize}
\item[]
	\ressubheading{Charter Communications}{Denver, CO}{Senior Platforms Engineer}{Feb 2020 -- Nov 2021}
	\begin{itemize}
	    \resitem{Reduced incident resolution times in CDN server group  by +95\% by delivering a data pipeline to ingest, enrich, and aggregate +15 billion log lines per day from all CDN servers.}
	    
	    \resitem{Led major version upgrade of Terraform infrastructure code repository containing over 50 apps and supporting major AWS infrastructure with zero downtime.}
	    
	    \resitem{Increased stability of hourly ETL batch job by +95\% by tuning Spark JVM settings and EMR cluster configuration settings.}
	    
	\end{itemize}

\item[]
	\ressubheading{DynAgility LLC.}{Ashburn, VA}{Software Engineer - AWS Solutions Architect Associate}{Mar 2018 -- Jan 2020}
	\begin{itemize}
	    \resitem{Added over \$1,000,000 of new contracts for client by building a pipeline which extracted TBs of raw data to AWS S3, transformed the data using Apache Spark jobs (Java) deployed in AWS EMR, and loaded the data into AWS Redshift and PostgreSQL backing a web application.}
	    
	    \resitem{Decreased customer's monthly AWS expenditures by converting data storage layer from Solr to AWS Redshift.}
	    
	\end{itemize}
	
\item[]
	\ressubheading{Reinventing Geospatial Inc.}{Fairfax, VA}{Software Engineer Intern}{Aug 2016 -- Dec 2016}

\item[]
	\ressubheading{Check Point Software Technologies}{Rockville, MD}{Incident Response Intern}{Jun 2016 -- Aug 2016}

\end{itemize}

\vspace{-0.2in}

\resheading{Education}
\vspace{-0.2in}
\begin{itemize}
\item[] 
    \ressubheading{Virginia Tech}{Blacksburg, VA}{B.S. Computer Science}{Graduated 2017}
    \begin{itemize}
        \resitem{Coursework: Theory of Data Structures \& Algorithms, Systems \& Networking Capstone, Java Cloud Applications, Principles of Computer Security, Cryptography}{}
        \resitem{Technologies: Java, C, Android, Windows, Linux}
    \end{itemize}
\end{itemize}

\vspace{-0.15in}

\resheading{Interests}
\vspace{-0.2in}
\begin{itemize}
    \item[] {\textbf{Swing Dancing}}
    \vspace{-0.05in}
    \begin{itemize}
        \item {Taught over 200 hours of classes and private lessons in vintage swing dance styles of Lindy Hop, Balboa, Charleston, and Solo Jazz.}
        \item {Founding member and staff member of New Columbia Swing.}
    \end{itemize}
\end{itemize}

\end{document}
